### 2011-05-29 thesis/novelty-intro.tex
Added comment on wrong proof of novelty as threshold.

Therefore any novelty system that decides to acknowledge a sample
$a$ as novel should also detect novelty on any sample $b$ satisfying
$P(\overline{novel}|b) < P(\overline{novel}|a)$.
As that always reduce the error probability described in
\autoref{eq:false-positive} as shown:

>>>>

Theres a problem with this proof. I need to review it. The original explanation
for me to model it as a threshold function required to have both true positive
and false positive ratios. But for the paper I though I could do it with only
the FPR, but its clear wrong.

Therefore any novelty system that considers to acknowledge a sample
$a$ as novel should before detect novelty on any sample $b$ satisfying
$P(\overline{novel}|b) < P(\overline{novel}|a)$.
As that would always yield a reduced the error probability described in
\autoref{eq:false-positive} as shown:
